Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-07 paper/ms.tex
improve abstract

% 250 word max!
\begin{abstract}
  %
  Complex periodic variables (CPVs) are stars that exhibit sharp and
  periodic optical light curves.  Previous work has indicated that such stars
  tend to be disk-free pre-main-sequence M dwarfs with rotation
  periods of 0.2--2 days.  To advance understanding of these enigmatic
  objects, we performed a blind search using TESS 2-minute data of
  \nstarssearched\ K and M dwarfs with $T$$<$16 and $d$$<$150\,pc.  We
  found \ngoods\ high-quality CPVs.  The new objects include the
  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
  oldest ($\approx$200\,Myr) CPVs known.  All objects but one turned
  out to be likely members of stellar associations, which enabled
  age-dating.  An exceptional new object, LP 12-502, showed up to
  eight flux dips per cycle; some of the LP 12-502 dips coexisted with slightly
  different periods, and the shortest-duration LP 12-502 dips matched the expected
  timescale for transiting small bodies at the corotation radius.
  Broadly, our search confirms
  that CPVs are mostly young ($\lesssim$150\,Myr) and low-mass
  ($\lesssim$0.4\,$M_\odot$).  The flux dips that embody the class
  have lifetimes of $\approx$100 cycles, and the dips collapse following
  stellar flares once every few months.  Corotating
  concentrations of gas or dust remains the only plausible explanation
  known.  The gas or dust is probably entrained by the star's magnetic
  field, and the sharp features could result from a multipolar field
  topology, a hypothesis supported by correspondences between the
  light curves of CPVs and of B stars known to have multipolar
  magnetic fields.
  %
\end{abstract}

>>>>

% 250 word max!
\begin{abstract}
  %
  Complex periodic variables (CPVs) are stars that exhibit sharp and
  periodic optical light curves.  Previous studies have indicated that
  these stars are typically disk-free pre-main-sequence M dwarfs with
  rotation periods ranging from 0.2 to 2 days.  To advance our
  understanding of these enigmatic objects, we conducted a blind
  search using TESS 2-minute data of \nstarssearched\ K and M dwarfs
  with $T$$<$16 and $d$$<$150\,pc.  We found \ngoods\ high-quality
  CPVs, and subsequently determined that most are members
  of stellar associations.  Among the new discoveries are the
  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
  oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
  12-502, exhibited up to eight flux dips per cycle. Some of these
  dips coexisted with slightly different periods, and the
  shortest-duration LP 12-502 dips precisely matched the expected
  timescale for transiting small bodies at the corotation radius.
  Broadly, our search confirms that CPVs are mostly young
  ($\lesssim$150\,Myr) and low-mass ($\lesssim$0.4\,$M_\odot$).  The
  flux dips characteristic of the class have lifetimes of $\approx$100
  cycles, although stellar flares seem to induce sudden dip collapse
  once every few months.  The most plausible explanation for these
  phenomena remains corotating concentrations of gas or dust.  The gas
  or dust is probably entrained by the star's magnetic field, and the
  sharp features could result from a multipolar field topology, a
  hypothesis supported by correspondences between the light curves of
  CPVs and of B stars known to have multipolar magnetic fields.
  %
\end{abstract}
